\begin{thebibliography}{7}
%

\bibitem{paper:1}
Halil Savuran and Murat Karakaya: ``A novel solution for routing a swarm of drones operated on a mobile host.''
Engineering Applications of Artificial Intelligence 138, 109337 (2024).
\url{https://doi.org/10.1016/j.engappai.2024.109337}

\bibitem{paper:2}
Gökhan Şengül, Murat Karakaya, Sanjay Misra, Olusola O. Abayomi-Alli, and Robertas Damaševičius:
``Deep learning based fall detection using smartwatches for healthcare applications.''
Biomedical Signal Processing and Control 71, 103242 (2022).
\url{https://doi.org/10.1016/j.bspc.2021.103242}

\bibitem{paper:3}
Tolga Üstünkök and Murat Karakaya: ``SS-MLA: a semisupervised method for multi-label annotation of remotely sensed images.''
Journal of Applied Remote Sensing 15(03), 036509 (2021).
\url{https://doi.org/10.1117/1.JRS.15.036509}

\bibitem{paper:4}
Murat Karakaya, M. Eryilmaz, and U. O. Ceyhan:
``Analyzing students' Academic Success in Prerequisite Course Chains:''
International Journal of Engineering Education 34(2A), 364--370 (2018).
No reliable Crossref match found; DOI unavailable.

\bibitem{paper:5}
Halil Savuran and Murat Karakaya: ``Efficient route planning for an unmanned air vehicle deployed on a moving carrier.''
Soft Computing 20(7), 2905--2920 (2016).
\url{https://doi.org/10.1007/s00500-015-1970-4}

\bibitem{paper:6}
Murat Karakaya: ``MSCT: An Efficient Data Collection Heuristic for Wireless Sensor Networks with Limited Sensor Memory Capacity.''
KSII Transactions on Internet and Information Systems 9(9), 3396--3411 (2015).
\url{https://doi.org/10.3837/tiis.2015.09.007}

\bibitem{paper:7}
Murat Karakaya: ``Time-Sensitive Ant Colony Optimization to Schedule a Mobile Sink for Data Collection in Wireless Sensor Networks.''
Ad Hoc \& Sensor Wireless Networks 28(1--2), 65--82 (2015).
No reliable Crossref match found; DOI unavailable.

\end{thebibliography}
